### 2025-07-30 docs/article/Sections/results.tex
Fix paragraph.

Their results show that Quarkus with Virtual Threads outperformed the
traditional thread-per-request model under increased concurrency. Moreover,
compared to the reactive model, virtual threads demonstrated competitive
performance, particularly when executing blocking operations within template
engines. In contrast, our experiments revealed that the reactive approach
underperforms relative to virtual threads, likely due to the significantly
larger number of data bindings in our use cases—namely, the
\texttt{Presentation} and \texttt{Stock} models.

>>>>

Their results show that Quarkus with Virtual Threads outperformed the
traditional thread-per-request model under increased concurrency. Moreover,
compared to the reactive model, virtual threads demonstrated competitive
performance, particularly when executing blocking operations within template
engines.
In contrast, our experiments revealed that the reactive approach in Spring
WebFlux performs better than virtual threads in the same experiment conducted
with Quarkus, suggesting that WebFlux provides a more efficient infrastructure
for managing reactive processing flows.
